|

### 2023-02-08 paper.Rmd
autogit

<!-- TODO: Disclaimer, Run-time is implementation dependent, no GPU use, etc... -->

@@

```{r airfoil-runtime-total, echo=FALSE, fig.cap="Median Runtime - Airfoil", out.width="80%"}
knitr::include_graphics("./img/airfoil_2hl_150hn_fullRun_30gens_TimeBenchmark/median_runtime.png")
```

>>>>

@@

```{r airfoil-runtime-total, echo=FALSE, fig.cap="Median Runtime - Airfoil", out.width="80%"}
knitr::include_graphics("./img/airfoil_2hl_150hn_fullRun_30gens_TimeBenchmark/median_runtime.png")
```
Figure \@ref(fig:airfoil-runtime-boxplot) shows the distribution of the total runtime for both DAE-GP variants. It shows that Pre-Training, besides largely increasing the median runtime, also leads to a higher dispersion which is shown by both a larger interquartile range as well as by a a standard deviation that increases by a factor of `r round(782.68 / 635.04, 3)` from 635,04 for regular DAE-GP to 782,68 for pre-trained DAE-GP.

```{r airfoil-runtime-boxplot, echo=FALSE, fig.cap="Total Runtime Boxplot - Airfoil", out.width="80%"}
knitr::include_graphics("./img/airfoil_2hl_150hn_fullRun_30gens_TimeBenchmark/total_runtime_distribution_boxplot.png")
```

### 2023-02-08 paper.tex
autogit

Johannes Gutenberg University Mainz}
\author{}
\date{\vspace{-2.5em}Date of Submission: 2023-02-06}

@@

@@

Figure \ref{fig:symReg-LevDiv} shows the median levenshtein edit distance as a metric for population diversity over the evolutionary search.

>>>>

Johannes Gutenberg University Mainz}
\author{}
\date{\vspace{-2.5em}Date of Submission: 2023-02-08}

@@

Figure \ref{fig:airfoil-runtime-boxplot} shows the distribution of the total runtime for both DAE-GP variants. It shows that Pre-Training, besides largely increasing the median runtime, also leads to a higher dispersion which is shown by both a larger interquartile range as well as by a a standard deviation that increases by a factor of 1.232 from 635,04 for regular DAE-GP to 782,68 for pre-trained DAE-GP.

{\centering \includegraphics[width=0.8\linewidth]{./img/airfoil_2hl_150hn_fullRun_30gens_TimeBenchmark/total_runtime_distribution_boxplot}

\caption{Total Runtime Boxplot - Airfoil}\label{fig:airfoil-runtime-boxplot}
\end{figure}

@@

Figure \ref{fig:symReg-LevDiv} shows the median levenshtein edit distance as a metric for population diversity over the evolutionary search. It clearly shows that pre-training does increase the population diversity for DAE-GP consistently for all tested benchmark problems.
